Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-25 ms/main.tex
format multiline eqs; results overview

In the following sections, we determine the equilibria of the model, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
We then analyze the evolution of a modifier of the social association to determine the evolution of social association.
Finally, we demonstrate the application of the conditions derived in the previous sections to predict the outcomes of stochastic simulations in a spatial model.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{With Population Structure}

>>>>

In the following sections, we determine the equilibria of the model, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
We then analyze the evolution of a modifier of social association.
Finally, we demonstrate the application of the conditions derived in the previous sections to predict the outcomes of stochastic simulations in a structured population.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Population Structure}
